Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-19 cav2017/cav2017.tex
+ general architecture of the synthesiser

\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}

@@

We investigate two different approaches of integrating solution generalisation 
into CEGIS:
\begin{itemize}
\item[1.] The first approach uses abstract acceleration to compute the set of reachable states, which 
enables abstraction refinement inside the CEGIS loop. 
\item[2.] The second approach relies on computing a completeness threshold $k$ for each loop such that it is sufficient to 
unroll the corresponding loop $k$ times. For this approach the generalisation step is given as an incremental
increase of precision and sampling rate.
\end{itemize}

@@

>>>>

\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows, patterns}

@@

We investigate two different approaches of integrating solution generalisation 
into CEGIS:
\begin{itemize}
\item[1.] The first approach uses abstract acceleration to compute the set of reachable states, which 
enables abstraction refinement inside the CEGIS loop. 
\item[2.] The second approach relies on computing a completeness threshold $k$ for each loop such that it is sufficient to 
unroll the corresponding loop $k$ times. For this approach the generalisation step is given as an incremental
increase of precision and sampling rate.
\end{itemize}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Architecture of the program synthesizer}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\label{synthesizer-general}
%
%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
% 
The input specification provided to the program synthesizer is of the form
$\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ where
$\vec{P}$ ranges over functions, $\vec{x}$ ranges over ground terms and
$\sigma$ is a quantifier-free formula.  We interpret the ground terms over
some finite domain $\mathcal{D}$.

The design of our synthesizer 
%is given in Figure~\ref{fig:CEGIS} and 
consists of two phases, an inductive synthesis phase and a validation phase,
%{\sc Synthesize} and {\sc Verify}, 
which interact via a finite set of test vectors {\sc inputs} that is updated incrementally. 
Given the aforementioned specification $\sigma$, the inductive synthesis
procedure
tries to find an existential witness $\vec{P}$ satisfying the specification
$\sigma(\vec{x}, \vec{P})$ for all $\vec{x}$ in {\sc inputs} (as opposed to
all $\vec{x} \in \mathcal{D}$).
%
If the synthesis phase succeeds in finding a witness~$\vec{P}$, this witness
is a candidate solution to the full synthesis formula.  We pass this
candidate solution to the validation phase, which checks whether it is a full
solution (i.e., $\vec{P}$ satisfies the specification $\sigma(\vec{x},
\vec{P})$ for all $\vec{x}\in\mathcal{D}$).
%
%determines whether
%it does satisfy the specification on all inputs by checking
%satisfiability of the following verification formula:
%
%$\exists \vec{x} . \lnot \sigma(\vec{x}, \vec{P})$
%If this formula is unsatisfiable, 
%% the candidate solution is in fact a 
%% full solution.
%
If this is the case, then the algorithm terminates.  Otherwise, additional
information is provided to the inductive synthesis phase in the form of a new
counterexample that is added to the {\sc inputs} set and the loop iterates
again.
%% the witness $\vec{x}$ denote an input on which the
%% candidate solution fails to meet the specification.  Thus, $\vec{x}$ is
%% added to the {\sc inputs} set, and the loop iterates again.

It is
worth noting that each iteration of the loop adds a new input to the
finite set $\text{\sc inputs}$ that is used for synthesis.  Given that
the full set of inputs $\mathcal{D}$
%\blue{[which by now should have a name, as suggested to be introduced above]} 
is finite, this means that the refinement loop
can only iterate a finite number of times.

@@

% \begin{figure*}[htb]
% \centering
% %\resizebox{1\textwidth}{!}
% {
%  \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
%   \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
% },
%           row sep=.6cm, column sep=2cm] {
%    \coordinate (aux1);
%    \& \coordinate (aux2);
%    \&;\\
%    \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
%    \&
%    complexnode/.pic={ 
%      \node[rectangle,draw,dotted,
% 	minimum width=7cm,
% 	minimum height=1cm,
%         pattern=north west lines, pattern color=gray!20,
% 	label={\sc Verify},] (verif) {};
%      \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc Uncertainty}};
%      \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=2cm]verif.center) {{\sc Precision}};
%    } 
%    \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
%    %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
%    %% \&
%    %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
%    \& \\
%    \node[minimum height=0.5cm] (gp) {\sf Closed-loop System Search};
%    \&
%    complexnode/.pic={ 
%      \coordinate (aux);
%    \node[minimum height=0.5cm] (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based Verifier};
%    \node[minimum height=0.5cm] (fp)  at ([xshift=2cm]aux.center) {\sf Fixed-point Arithmetic Verifier};
%    }   
%     \\
%   };

%    \path
%     ([yshift=2em]synth.east) edge node[xshift=-0.5em] {Candidate solution} ([yshift=2em]verif1.west)
%     ([yshift=-2em]verif1.west) edge node {Counterexample} ([yshift=-2em]synth.east)
%     ([xshift=5em]verif1.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]bmc.north)
%     ([xshift=5em]verif2.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]fp.north)
%     ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
%     ([xshift=-5em]fp.north) edge node[align=center]  {True/\\False} ([xshift=-5em]verif2.south)
%     (verif2) edge node {} (done)
%     ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
%     ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\candidate} ([xshift=-5em]synth.south)
%     (aux1) edge (synth.north);
%    \path[-]
%    (verif2.north) edge node[align=center] {} ([xshift=6.7cm]aux2)
%    ([xshift=6.7cm]aux2) edge node[align=center] {Increase Precision} (aux1);

%  \end{tikzpicture}
% }
% \caption{The CEGIS loop with precision and sampling rate incrementation}
% \label{fig:CEGIS}}
% \end{figure*}
